### 2015-06-07 LOI/inc2.tex
minor changes to wording

\underline{\textbf{Objectives:}} Exascale scientific discovery will be
severely bottlenecked without sufficient new research into managing and
storing the large amounts of data that will be produced during the
simulation, and analyzed for months afterwards.  Our goal in this project is
to address the associated I/O and storage challenges in the context of
current ancd emerging storage landscapes, and expedite insights into mission
critical scientific processes. To that end, we will build on the
capabilities offered by ADIOS and DataSpaces that provide I/O abstractions
and services, the Sirocco peer-to-peer file system under development at
Sandia and the object storage and annotation expertise of UC Santa Cruz, to
explore application and multi-tier storage aware data management
solutions. Our solutions will provide novel functionalities and APIs for
% It will center upon a multi-tier storage-aware approach and incorporate new
% functionalities, extended object metadata and APIs for

%
1) specifying, at the application level, data annotations that enable the
qualification of the relative importance and utility of data objects, and
enable them to be mapped at runtime to appropriate storage capabilities
across the storage hierarchy;
%
2) specifying selectable performance/quality/cost tradeoffs from both the
application and system perspectives; and
%
3) evaluating these tradeoffs at runtime during data placement and movement,
and executing the resultant policies in an autonomic system using models,
heuristics and continous learning,
%
4) Leveraging techniques such as application-aware data compression (both
lossy with specified error bounds and lossless), re-computation at the
requisite level of accuracy, and I/O prioritization to enforce these
policies.
%  2) a selectable performance/quality tradeoff when reading data, and
  %  the ability to recompute data if needed, and
  %  3) incorporate reader prioritization for data annotation, placement, and data
  %  quality when writing data.  
A key challenge in this project is defining and maintaining the metadata
connecting different object quality and utility levels, and using this metadata 
to most appropriately manage the placement and access of data object based on 
user/application intent/contraints and storage system state.
% to best enabling the user with the best possible outcomes 
% given the user intent and the storage system state. 
The new user APIs required to interact with this rich metadata system will
drive effective use of the entire middleware and storage stack.  The project
is comprised of a team with strong expertise in I/O middleware (ORNL,
Rutgers), file system (SNL, UCSC) and storage (UCSC), and connect and
coordinate these key storage components in a seamless fashion.

@@

\hasan{Since we are laying the foundation for a real storage system we can't
  be solving the problem for a single application. We will eventually have
  to consider things like fairness, availability and this is also why we
  want to tie in with the resource management system} 
%
Our objective here is to reduce the time to knowledge, not just for a single
application or workflow, but for the entire workload in the system. This is
an end-to-end metric relevant to the scientific discovery process. We will
explore beyond the traditional high volume I/O pattern of
checkpoint/restart, and will address the challenges posed by other essential
data access patterns in the knowledge gathering process.  Through a deeper
insight into the scientific process we will encode and utilize accuracy and
errors as optimization parameters.  For example, scientific simulations
contain approximations, as do measurements from observations and
experiments, and depending on the goal, these approximations are
acceptable. We can leverage this observation to optimize the presentation of
data to the user and to implement various tradeoffs -- users can ask for
information within a given accuracy bound, allowing us to offer a mode for
re-computation vs. data storage and retrieval.

%  
\TODO{\bf: please list other things from OLCF}
%

>>>>

\underline{\textbf{Objectives:}} Exascale scientific discovery will be
severely bottlenecked without sufficient new research into managing and
storing the large amounts of data that will be produced during the
simulation, and analyzed for months afterwards.  Our goal in this project is
to address the associated I/O and storage challenges in the context of
current ancd emerging storage landscapes, and expedite insights into mission
critical scientific processes. To that end, we will build on the
capabilities offered by ADIOS and DataSpaces that provide I/O abstractions
and services, the Sirocco peer-to-peer file system under development at
Sandia and the object storage and annotation expertise of UC Santa Cruz, to
explore application and multi-tier storage aware data management
solutions. Our solutions will provide novel functionalities and APIs for
% It will center upon a multi-tier storage-aware approach and incorporate new
% functionalities, extended object metadata and APIs for 
%
1) specifying, at the application level, data annotations that enable the
qualification of the relative importance and utility of data objects, and
enable them to be mapped at runtime to appropriate storage capabilities
across the storage hierarchy;
%
2) specifying selectable performance/quality/cost tradeoffs from both the
application and system perspectives; and
%
3) evaluating these tradeoffs at runtime during data placement and movement,
and executing the resultant policies in an autonomic system using models,
heuristics and continous learning,
%
4) Leveraging techniques such as application-aware data compression (both
lossy with specified error bounds and lossless), re-computation at the
requisite level of accuracy, and I/O prioritization to enforce these
policies.
%  2) a selectable performance/quality tradeoff when reading data, and
  %  the ability to recompute data if needed, and
  %  3) incorporate reader prioritization for data annotation, placement, and data
  %  quality when writing data.  
A key challenge in this project is defining and maintaining the metadata
connecting different object quality and utility levels, and using this metadata 
to most appropriately manage the placement and access of data object based on 
user/application intent/contraints and storage system state.
% to best enabling the user with the best possible outcomes 
% given the user intent and the storage system state. 
The new user APIs required to interact with this rich metadata system will
drive effective use of the entire middleware and storage stack.  The project
is comprised of a team with strong expertise in I/O middleware (ORNL,
Rutgers), file system (SNL, UCSC) and storage (UCSC), and connect and
coordinate these key storage components in a seamless fashion.

@@

\hasan{Since we are laying the foundation for a real storage system we can't
  be solving the problem for a single application. We will eventually have
  to consider things like fairness, availability and this is also why we
  want to tie in with the resource management system} 
%
Our objective here is to reduce the time to knowledge, not just for a single
application or workflow, but for the entire workload in the system. This is
an end-to-end system wide metric relevant to the scientific discovery
process. We will explore beyond the traditional high volume I/O pattern of
checkpoint/restart, and will address the challenges posed by other essential
data access patterns in the knowledge gathering process.  Through a deeper
insight into the scientific process we will encode and utilize accuracy and
errors as optimization parameters.  For example, scientific simulations
contain approximations, as do measurements from observations and
experiments, and depending on the goal, these approximations are
acceptable. We can leverage this observation to optimize the presentation of
data to the user and to implement various tradeoffs -- users can ask for
information within a given accuracy bound, allowing us to offer a tradeoff for
re-computation vs. data storage and retrieval.

%  
% \TODO{\bf: please list other things from OLCF}
%
